---
title: "Plotting Methods"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plotting Methods}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Plotting Methods

In this article, we provide more detail on the different plots for the 
interpretability methods, including how to set the number of points plotted 
for a given feature, setting the center of the plots, and additional options not 
discussed in the general overview. 

### Interpreter Class Initialization

For the examples in the additional articles, we use the well-known `iris` dataset, 
which provides information on 50 flowers from each of 3 species of iris, and 
a random forest model for predicting the `"Sepal.Length"` variable. To begin 
making interpretability plots, we must start with an `Interpreter` object, 
which consists of the following parameters:

```{r}
library(MASS)
library(Distillery)
library(Rforestry)

# Load in data 
data("iris")
set.seed(491)
data <- iris

# Train a random forest on the data set
forest <- forestry(x=data[,-1],
                   y=data[,1])

# Create a predictor wrapper for the forest
forest_predictor <- Predictor$new(model = forest,
                                  data=data,
                                  y="Sepal.Length",
                                  task = "regression")

# We specify grid.size for clarity (grid.size = 50 by default)
forest_interpreter <- Interpreter$new(forest_predictor,
                                      grid.size = 50)
print(forest_interpreter)
```

The following parameters in the `Interpreter` object determine different aspects 
of the interpretability plots:

* `grid.size`: This provides the number of grid points we want for continuous 
               features for PDP, ICE, and ALE methods. A larger input for `grid.size`
               creates more points that are plotted, which increases the fidelity 
               of the plot and the computation time. This is specified when the 
               `Interpreter` object is declared.
* `grid.points`: This stores lists of grid points for each feature in the data. 
                 For continuous features, the grid points are equally spaced 
                 values from the minimum value to maximum value of the feature, 
                 with the length specified by `grid.size`. This parameter determines 
                 which points to plot PDP and ICE methods.
* `center.at`: This stores a list of values to center the continuous features plotted
               for PDP and ICE curves. The center is defined as the value for a 
               feature that we want to center at, rather than a particular value 
               for the PDP or ICE curve. By default, this is set to the minimum 
               value in the `grid.points` list for each continuous feature. 
               
Below, we demonstrate examples of these parameters for feature `Sepal.Width`:

```{r}
# The values of Sepal.Width to be plotted by PDP and ICE curves
print(forest_interpreter$grid.points$Sepal.Width)

# The number of grid.points is equal to the grid.size
print(length(forest_interpreter$grid.points$Sepal.Width))
print(forest_interpreter$grid.size)

# The value of Sepal.Width we center the PDP and ICE curves
print(forest_interpreter$center.at$Sepal.Width)

# plot the PDP and ICE curves
plot(forest_interpreter, features = "Sepal.Width")
```

After initializing the `Interpreter`, we can still change the centers and grid 
points of the plot. For example, we provide some code below to provide a new set 
of grid points and center at the mean value for `Sepal.Width`. Note that when 
we set a new center value, it must be within the range of the grid points.

```{r}
# Set new grid points
set.grid.points(forest_interpreter, "Sepal.Width", 
                values = seq(2, 4.5, length.out = 100))

# Set new center
set.center.at(forest_interpreter, "Sepal.Width", 
              mean(seq(2, 4.5, length.out = 100)))

# New plot
plot(forest_interpreter, features = "Sepal.Width")

```

In contrast to the fixed grid points for PDP and ICE methods, the ALE method 
sets its grid points based on quantiles of the marginal distribution. 
By doing so, it avoids sparsity within any one neighborhood. The ALE is also 
always mean-centered. As a result, methods such as `set.grid.points` and 
`set.center.at` do not affect the ALE plots. The key parameter for the ALE method 
is `grid.size`, which determines the number of points calculated by the ALE. 

```{r}
# ALE plot
plot(forest_interpreter, features = "Sepal.Width", method = "ale")
```

### Additional Features for ICE Methods: Clustering

This package also provides a new feature to cluster the ICE curves. The default 
option of `plot` for the `Interpreter` class plots the ICE curves and their mean, 
the `PDP` curve. We introduce the use of the `kmeans` unsupervised learning algorithm 
as a way to better visualize groups of ICE curves. To do so, we set `method = "ice"` 
in the `plot` function, and can set the number of clusters and the type of 
clustering with the `clusters` and `clusterType` arguments respectively. 

```{r}
# Clustering Based on the Predicted Values of the ICE Curves
plot(forest_interpreter,
     features = "Sepal.Width",
     method = "ice",
     clusters = 4,
     clusterType = "preds")

# Clustering Based on the Change in Predicted Values of the ICE Curves
plot(forest_interpreter,
     features = "Sepal.Width",
     method = "ice",
     clusters = 4,
     clusterType = "gradient")
```

The two options for `clusterType` differ as follows:
* `preds`: Each predicted value for an ICE curve is treated as an entry in a vector, 
           and the ICE curves as grouped based on these prediccted values. 
* `gradient`: Rather than clustering based on the predicted values, the gradient method 
              takes the change in predicted values across consecutive grid points, and 
              clusters based on these changes.
              
For further details on these methods, please refer to the "References" tab, which 
contains documentation for each of the methods discussed.




