---
title: "Local Surrogate"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Local Surrogate}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Local Surrogate Models for Bivariate PDP Functions

In some cases, it can be difficult to understand the output of a bivariate PDP function.
As an alternative to visualizing these functions, we can fit a small decision tree 
using the PDP function values as the outcomes and the two features (and possibly their
interaction) as the independent features. The `localSurrogate` function in this 
package provides a more comprehensive method for interpreting bivariate PDP results 
by both plotting the output of the bivariate predictions and returning a weak-learner 
decision tree. In this article, we demonstrate how to use the `localSurrogate` function, 
and how to specify different parameters of the weak learner returned.

```{r, include=FALSE, echo = FALSE, results='hide'}
# Load the required packages
library(distillML)
library(Rforestry)
library(ggplot2)
```

```{r, echo = TRUE}
# Load the required packages
library(distillML)
library(Rforestry)

# Load in data 
data("iris")
set.seed(491)
data <- iris

# Train a random forest on the data set
forest <- forestry(x=data[,-1],
                   y=data[,1])

# Create a predictor wrapper for the forest
forest_predictor <- Predictor$new(model = forest,
                                  data=data,
                                  y="Sepal.Length",
                                  task = "regression")

# Create the interpreter object
forest_interpret <- Interpreter$new(predictor = forest_predictor)
```

This method is implemented in the `localSurrogate()` function. The two arguments 
required are the `Interpreter` object, and a two-column dataframe where each row 
is a pair of feature names. The returned object consists of two distinct lists:

* plots: This list contains the bivariate PDP plots. For a pair of two continous 
         features, this returns a heatmap. For a pair of one continuous and one 
         categorical feature, this returns a conditional PDP plot, where the curves 
         are grouped based on the continuous feature value.
* models: This list contains the weak learners, which can make predictions and be 
          plotted for further visualization.

```{r, echo=TRUE}
# Make the bivariate PDP function
local.surr <- localSurrogate(forest_interpret,
                             features.2d = data.frame(col1 = c("Sepal.Width",
                                                               "Sepal.Width"),
                                                      col2 = c("Species",
                                                               "Petal.Width")))

# examples of the plot
plot(local.surr$plots$Sepal.Width.Species)
plot(local.surr$plots$Sepal.Width.Petal.Width)

# examples of the weak learner
plot(local.surr$models$Sepal.Width.Species)
plot(local.surr$models$Sepal.Width.Petal.Width)

```

We can also include the interation term between the pair of features by specifying 
the argument `interact` to `TRUE`. By default, this argument is `FALSE`. To 
change the parameters of the weak-learner, we can specify a list of parameters 
through the argument `params.forestry`. By default, the weak learner uses one 
tree, with a maximum depth of 2. Below, we demonstrate how one might use these 
arguments by including interactions and letting the tree grow to a maximum depth 
of 3.

```{r}
# Include interactions and let the maximum depth be 3
local.surr <- localSurrogate(forest_interpret,
                             features.2d = data.frame(col1 = c("Sepal.Width"),
                                                      col2 = c("Petal.Width")),
                             interact = T,
                             params.forestry = list(ntree = 1, maxDepth = 3))

# Plot the resulting local surrogate model
plot(local.surr$models$Sepal.Width.Petal.Width)

```

For further details, please refer to the documentation on `localSurrogate` provided in 
the "References" section.



